---
title: "Assignment 6"
author: "Apurva Hari"
date: "August 9, 2016"
output: pdf_document
---

##### 2.  If you're feeling more adventurous, try the code from Chapter 8 in Kabacoff's R In Action, which offers further diagnostics and more exploration related to linear regression, such as doing cross-validation or trying to evaluate the relative importance of predictors. Not all of it will work; in particular, I think some of the functions in the "car" package are deprecated. Try FOUR from the following:

#### Listing 8.6
#### Function for plotting studentized residuals

``` {r}

states <- as.data.frame(state.x77[,c("Murder","Population","Illiteracy","Income",
                                     "Frost")])
fit <- lm(Murder ~ Population + Illiteracy + Income + Frost, data = states )

residplot <- function(fit,nbreaks =10) {
      
        z <-rstudent(fit)
        hist(z,breaks=nbreaks,freq= FALSE, xlab ="Studentized Residual",
        main = "Distribution of Errors")
        rug(jitter(z),col ="brown") 
        curve(dnorm(x,mean =mean(z),sd =sd(z)),
        add = TRUE, col ="blue" ,lwd = 2)
        lines(density(z)$x,density(z)$y,
        col ="red",lwd = 2, lty = 2)
        legend("topright", 
        legend = c("Normal Curve", "Kernel Density Curve"),
        lty = 1:2, col =c("blue","red"), cex =.7)
}

residplot(fit)
```
#### Listing 8.8
####Global Test of Linear Model Assumptions

```{r}


library(gvlma)
gvmodel <- gvlma(fit)

summary(gvmodel)
gvlma(x=fit)

```

#### Listing 8.11 
#### Comparing nested models using anova()

```{r}


states <- as.data.frame(state.x77[,c("Murder","Population","Illiteracy","Income",
                                     "Frost")])
fit1 <- lm(Murder ~ Population + Illiteracy + Income + Frost, data = states )
fit2 <- lm(Murder ~ Population + Illiteracy, data = states )

anova(fit2,fit1)
```

#### Listing 8.12 
#### Comparing models with AIC

``` {r}


states <- as.data.frame(state.x77[,c("Murder","Population","Illiteracy","Income",
                                     "Frost")])
fit1 <- lm(Murder ~ Population + Illiteracy + Income + Frost, data = states )
fit2 <- lm(Murder ~ Population + Illiteracy, data = states )

AIC(fit2,fit1)

```
